### 2013-03-28 doc/sosp13/memory.tex
Update memory api.

\begin{figure}[htbp]
  \begin{center}
    \begin{minipage}{\columnwidth}
	\small
	\begin{tabular}{l}
      	\texttt{\scriptsize global\_address global\_malloc( size )} \\
      	\texttt{\scriptsize global\_free( global\_address )} \\ 
      	Allocation in the global heap \\ \\
      	\texttt{\scriptsize delegate\_read( global\_address, local\_var )}  \\
      	\texttt{\scriptsize delegate\_read\_async( global\_address, local\_var )}  \\
      	\texttt{\scriptsize delegate\_write( global\_address, local\_var )} \\
      	\texttt{\scriptsize delegate\_write\_async( global\_address, local\_var )} \\
      	\texttt{\scriptsize delegate\_cas( global\_address, local\_var )} \\
      	\texttt{\scriptsize delegate\_fetch\_inc( global\_address, local\_var )} \\
      	\texttt{\scriptsize delegate\_fetch\_inc\_async( global\_address, local\_var )} \\ 
      	Memory operations at the home core of a global address \\ \\
      	\texttt{\scriptsize cache\_acquire( global\_address, local\_buf, \{RO,RW,WO\})} \\
      	\texttt{\scriptsize cache\_release( global\_address, local\_buf )} \\ 
		Perform cache operations to acquire/release global data.  \\
		Acquire copies all data to local node and returns a pointer. \\ 	
		Release optionally copies data back to global memory. \\
	\end{tabular}
      \caption{\label{fig:accessing-memory} \Grappa API for memory accesses.}     \end{minipage}
  \end{center}
\end{figure}

@@

% We restrict the use of delegate operations in order to make them also
% useful for synchronization operations.

@@

% \TODO{Talk about synchronous and asynchronous delegate operations. Talk about global completion object. Should we have a whole section on synchronization?}
% \TODO{If we do want a section on GlobalCompletionEvent:
%   \begin{itemize}
%     \item many tasks and operations in the applications we've implemented do not need immediate consistency
%     \item guaranteeing ordering requires blocking a task. this is unavoidable if the task relies on the returned value, or if one task is dependent on others
%     \item however, much of the applications we've implemented (and other big-data things) are data-parallel, so tasks within a data-parallel loop can run in any order
%     \item in addition, often these data-parallel tasks will update values that aren't used until the next data-parallel loop
%     \item this allows us to free up workers/stacks (running out of stacks causes  latency-sensitivity because we can't continue until tasks complete)
%     \item must guarantee all operations that were supposed to happen in the loop complete before continuing, including tasks and delegate operations
%     \item \emph{motivating example:} write to array in one loop, use updated values in next loop (could also mention the ``PushBuffer'' example where we buffer queue appends because the order in the queue doesn't matter)
%     \item GlobalCompletionEvent is complicated by task-stealing and the fact that delegate operations complete on a different core than they started, forcing us to use a ``cancelable barrier''-like approach (possible citation: Ravichandran, et al. ``Work stealing for multi-core HPC Clusters'')
%     \item interface to GlobalCompletionEvent:
%       \begin{itemize}
%         \item \texttt{gce.enroll(n)}: enroll n tasks/operations to be done, when goes from 0 to 1, leave cancelable barrier
%         \item \texttt{gce.complete(n)}: complete tasks, when it goes to zero, enter global cancelable barrier
%         \item \texttt{gce.wait()}: block until all cores have no work
%       \end{itemize}
%     \item to prevent early wakeups, stolen tasks must send a completion message back to the core they were started on
%   \end{itemize}
% }

@@

% \TODO{Not sure this warrants its own paragraph, seems like the explicit caches are just the same as reading and then writing using delegates.}

>>>>

\begin{figure}[htbp]
  \begin{center}
    \begin{minipage}{\columnwidth}
	\small
	\begin{tabular}{l}
      	\texttt{\scriptsize GlobalAddress<T> global\_malloc<T>( size )} \\
      	\texttt{\scriptsize global\_free( GlobalAddress<T> )} \\ 
      	Allocation in the global heap \\ \\
      	\texttt{\scriptsize delegate\_read( GlobalAddress<T>, T )}  \\
      	\texttt{\scriptsize delegate\_read\_async( GlobalAddress<T>, T )}  \\
      	\texttt{\scriptsize delegate\_write( GlobalAddress<T>, T value)} \\
      	\texttt{\scriptsize delegate\_write\_async( GlobalAddress<T>, T )} \\
      	\texttt{\scriptsize delegate\_cas( GlobalAddress<T>, T, T )} \\
      	\texttt{\scriptsize delegate\_fetch\_inc( GlobalAddress<T>, T )} \\
      	\texttt{\scriptsize delegate\_fetch\_inc\_async( GlobalAddress<T>, T )} \\ 
      	Memory operations at the home core of a global address \\ \\
      	\texttt{\scriptsize cache\_acquire( GlobalAddress<T>, local\_buf, \{RO,RW,WO\})} \\
      	\texttt{\scriptsize cache\_release( GlobalAddress<T>, local\_buf )} \\ 
		Perform cache operations to acquire/release global data.  \\
		Acquire copies all data to local node and returns a pointer. \\ 	
		Release optionally copies data back to global memory. \\
	\end{tabular}
      \caption{\label{fig:accessing-memory} \Grappa API for memory accesses.}     \end{minipage}
  \end{center}
\end{figure}

@@

@@

@@
